---
title: "Distribution of Income, Wealth, and Mortgage during Retirement in SCF"
author: "Alan Lujan"
date: "6/15/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(ggplot2)
library(ggthemes)
library(haven)
library(tidyverse)

SCF <- read_dta("scf_nb.dta")
SCF$agecl <- as.numeric(SCF$Age_grp)
SCF <- as_factor(SCF)
```

### Joint Density of log Permanent Income and log Normalized Wealth

```{r}
p <- ggplot(
  SCF %>%
    filter(agecl %in% seq(9, 12)),
  aes(x = lnPermIncome, y = lnNrmWealth)
) +
  geom_density_2d() +
  facet_grid(Age_grp ~ Educ) +
  theme_bw()
print(p)
```

\newpage 

### Distribution of log Normalized Wealth

```{r}
p <- ggplot(
  SCF %>%
    filter(agecl %in% seq(9, 12)),
  aes(x = lnNrmWealth, weight = wgt)
) +
  geom_density() +
  facet_grid(Age_grp ~ Educ) +
  theme_bw()
print(p)
```

\newpage

### Distribution of log Permanent Income

```{r}
p <- ggplot(
  SCF %>%
    filter(agecl %in% seq(9, 12)),
  aes(x = lnPermIncome, weight = wgt)
) +
  geom_density() +
  facet_grid(Age_grp ~ Educ) +
  theme_bw()
print(p)
```

\newpage

### Distribution of log Normalized Mortgage

```{r}
p <- ggplot(
  SCF %>%
    filter(agecl %in% seq(9, 12)),
  aes(x = lnNrmMortgage, weight = wgt)
) +
  geom_density() +
  facet_grid(Age_grp ~ Educ) +
  theme_bw()
print(p)
```

\newpage

### Mean log Normalized Wealth by age and education

```{r}
p <- ggplot(
  SCF,
  aes(y = lnNrmWealth, x = age, weight = wgt, group = Educ, color = Educ)
) +
  geom_smooth() +
  theme_bw()
print(p)
```

\newpage

### Mean Normalized Wealth by age and education

```{r}
p <- ggplot(
  SCF,
  aes(y = NrmWealth, x = age, weight = wgt, group = Educ, color = Educ)
) +
  geom_smooth() +
  theme_bw()
print(p)
```

\newpage

### Mean log Permanent Income by age and education 

```{r}
p <- ggplot(
  SCF,
  aes(y = lnPermIncome, x = age, weight = wgt, group = Educ, color = Educ)
) +
  geom_smooth() +
  theme_bw()
print(p)
```

\newpage

### Mean log Normalized Mortgage by age and education 

```{r}
p <- ggplot(
  SCF,
  aes(y = lnNrmMortgage, x = age, weight = wgt, group = Educ, color = Educ)
) +
  geom_smooth() +
  theme_bw()
print(p)
```

\newpage

### Mean log Normalized Wealth by age and homeownership class

```{r}
p <- ggplot(
  SCF,
  aes(y = lnNrmWealth, x = age, weight = wgt, group = hmort, color = hmort)
) +
  geom_smooth() +
  theme_bw()
print(p)
```

\newpage

### Mean log Normalized Wealth by age, homeownership class, and education

```{r}
p <- ggplot(
  SCF,
  aes(y = lnNrmWealth, x = age, weight = wgt, group = hmort, color = hmort)
) +
  geom_smooth() +
  facet_wrap(~Educ) +
  theme_bw()
print(p)
```

\newpage

### Mean log Permanent Income by age, homeownership class, and education

```{r}
p <- ggplot(
  SCF,
  aes(y = lnPermIncome, x = age, weight = wgt, group = hmort, color = hmort)
) +
  geom_smooth() +
  facet_wrap(~Educ) +
  theme_bw()
print(p)
```
